Leveraged Volume Sampling - Summary

### 2019-03-02 summary/paper-summary.tex
added results to the summary

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{mathtools}

@@

        The first property, when applied to $r=U^Tv^\ast - y$, allows us to bound $U^TQ_{\pi}r$ and the second allows us to bound $||(U^TQ_{\pi}U)^{-1}|| < 8$
        with high probability.

>>>>

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{graphicx}

@@

        The first property, when applied to $r=Uv^\ast - y$, allows us to bound $||U^TQ_{\pi}r||^2 \leq \epsilon\frac{k^2}{8^2}||r||^2$
        and the second allows us to bound $||(U^TQ_{\pi}U)^{-1}|| < 8$, both with high probability, there by yielding the bound:
        \begin{equation}
            L(w_{\pi}^\ast) \leq (1+\epsilon)L(w^\ast)
        \end{equation}

    \newpage
    \section{Numerical Results}
        I've done my best to replicate the results in the paper.
        The trend of diminishing error at relatively small number of rows is there but I couldn't replicate the smooth results the paper presented.

        \begin{figure}[h]
            \includegraphics[width=\linewidth]{results/abalone.png}
            \caption{abalone dataset.}
            \label{fig:dataset1}
        \end{figure}
        \begin{figure}[h]
            \includegraphics[width=\linewidth]{results/bodyfat.png}
            \caption{bodyfat dataset.}
            \label{fig:dataset1}
        \end{figure}
        \begin{figure}[h]
            \includegraphics[width=\linewidth]{results/cadata.png}
            \caption{cadata dataset.}
            \label{fig:dataset1}
        \end{figure}
        \begin{figure}
            \includegraphics[width=\linewidth]{results/cpusmall.png}
            \caption{cpusmall dataset.}
            \label{fig:dataset1}
        \end{figure}
        \begin{figure}
            \includegraphics[width=\linewidth]{results/housing.png}
            \caption{housing dataset.}
            \label{fig:dataset1}
        \end{figure}
        \begin{figure}
            \includegraphics[width=\linewidth]{results/mg.png}
            \caption{mg dataset.}
            \label{fig:dataset1}
        \end{figure}
